Childhood exposure to non-persistent endocrine disruptors, glucocorticosteroids, and attentional function: A cross-sectional study based on the parametric g-formula

### 2024-08-12 output/paper/_figures.qmd
Combining forest plots of RQ3 and RQ3SA.

  return(ret)
} # End function forest_plot
```

@@

```{r}
targets::tar_load(
  dplyr::matches("marginal_comparisons_(\\d)$"),
  store = store
)
```

@@

@@

obj3 <- tidy_res_meffects(
  df = marginal_comparisons_3,
  sa_var = NULL,
  outcome = c("hitrtse"),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj3, r = 5, is_cortisol = TRUE)
```
**Marginal contrasts on the logarithmic scale for the effect of an increase from the 10th to the 90th percentile of the glucocorticosteroids on {{< acr hitrtse first_use=true >}} expressed in {{< acr mss >}} (HELIX subcohort; 2013-2016).** 
Circles indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}. The size of the circles represents the *S* value of the effect estimate [@RafiGreenland:2020]. Abbreviations: cortisone production (cortisone prod.); cortisol production (cortisol prod.); corticost. prod. (corticosterone production).
:::

>>>>

  return(ret)
} # End function forest_plot

# Function to align forest plot with table numerical results for RQ and RQSA
forest_plot_combined <- function(obj, r = 4, is_cortisol = FALSE) {
  edcs <- myphd::edcs_information() |>
    dplyr::filter(!chem_id %in% c("dedtp", "dmdtp")) |>
    dplyr::select(chem_id, short_name, class) |>
    dplyr::bind_rows(
      tibble::tibble(
        chem_id = c("Exposure"),
        short_name = c("Exposure"),
        class = c(NULL)
      )
    )

  # From table of numerical results to ggplot object
  tbl_num_res <- obj$numerical_results |>
    dplyr::bind_rows(
      tibble::tibble(
        variable = "Exposure",
        val = "Marginal contrast (95% CI)",
        estimate = 100,
        outcome = "",
        class = "AAA",
        modifier = c(NA, NA, NA)
      ),
      tbl_num_res
    ) |>
    dplyr::group_by(class) |>
    dplyr::arrange(
      variable,
      .by_group = TRUE
    ) |>
    dplyr::ungroup() |>
    dplyr::mutate(
      variable = factor(variable, levels = unique(variable)),
      variable = forcats::fct_rev(variable)
    ) |>
    tidylog::select(-estimate) |>
    ggplot2::ggplot(
      ggplot2::aes(
        y = variable,
        shape = modifier
      )
    ) +
    ggplot2::geom_text(
      ggplot2::aes(
        x = 0,
        label = variable
      ),
      hjust = 0,
      fontface = "bold"
    ) +
    ggplot2::geom_text(
      ggplot2::aes(
        x = 1,
        label = val
      ),
      hjust = 0,
      position = ggstance::position_dodgev(height = 0.9)
    ) +
    ggplot2::theme_void() +
    ggplot2::theme(
      strip.background = ggplot2::element_blank(),
      strip.text = ggplot2::element_blank(),
      legend.position = "bottom",
      legend.box = "vertical",
      legend.margin = ggplot2::margin()
    ) +
    ggplot2::coord_cartesian(
      xlim = c(0, 4)
    )

  return(ret)
} # End function forest_plot_combined
```

@@

```{r}
targets::tar_load(
  dplyr::matches("marginal_comparisons_(\\d)$"),
  store = store
)
targets::tar_load(
  dplyr::matches("marginal_comparisons_3SA$"),
  store = store
)
```

@@

```{r}
marginal_comparisons_3$modifier <- "overall"
obj3 <- tidy_res_meffects(
  df = dplyr::bind_rows(marginal_comparisons_3, marginal_comparisons_3SA),
  sa_var = "e3_sex",
  outcome = c("hitrtse"),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig,
  combined = c("overall", "females", "males")
)
```

@@

forest_plot_combined(obj = obj3, r = 5, is_cortisol = TRUE)
```
**Marginal contrasts on the logarithmic scale for the effect of an increase from the 10th to the 90th percentile of the glucocorticosteroids on {{< acr hitrtse first_use=true >}} expressed in {{< acr mss >}}, overall and by sex (HELIX subcohort; 2013-2016).** 
Circles indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}. The size of the circles represents the *S* value of the effect estimate [@RafiGreenland:2020]. Abbreviations: cortisone production (cortisone prod.); cortisol production (cortisol prod.); corticost. prod. (corticosterone production).
:::

### 2024-08-12 output/paper/_si.qmd
Combining forest plots of RQ3 and RQ3SA.

::: {#supptbl-info-chems}
```{r info-chems}
edcs_info <- myphd::edcs_information() |>
  tidylog::select(-c(chem_id, smiles, ctd_id, exposome_explorer_id)) |>
  tidylog::mutate(
    var = janitor::make_clean_names(
      short_name,
      replace = c(`-` = ""),
      case = "none"
    ) |>
      tolower()
  ) |>
  tidylog::relocate(var, .after = short_name) |>
  dplyr::group_by(class) |>
  dplyr::arrange(
    short_name,
    .by_group = TRUE
  )
gt::gt(edcs_info,
       groupname_col = "class") |>
  gt::sub_values(
    values = c("NA"),
    replacement = ""
  ) |>
  gt::cols_label(
    full_name = "Compound",
    short_name = "Symbol",
    var = "Variable name",
    pubchem_cid = "PubChem CID",
    parental_compound = "Parental compound"
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  ) |>
  gt::tab_style(
    style = gt::cell_borders(
      weight = gt::px(0)
    ),
    locations = list(
      gt::cells_body(),
      gt::cells_stub(),
      gt::cells_row_groups()
    )
  )
```
**Information about non-persistent {{< acr edcs first_use=true >}}, including the full compound name, the standard symbol, the used variable name, the identifier from PubChem, and the parental compound.**
:::

@@

::: {#supptbl-marginal-3sa}
```{r marginal-3sa-tbl}
m3sa <- tidy_res_meffects(
  df = marginal_comparisons_3SA,
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)

m3sa$table
```
**Marginal contrasts on the logarithmic scale for effect modification by sex of a increase from the 10th to the 90th percentile of the glucocorticosteroids on {{< acr hitrtse first_use=true >}} expressed in {{< acr mss >}} (HELIX subcohort; 2013-2016).**
:::

>>>>

::: {#supptbl-info-chems}
```{r info-chems}
edcs_info <- myphd::edcs_information() |>
  tidylog::select(-c(chem_id, smiles, ctd_id, exposome_explorer_id, molar_mass)) |>
  tidylog::mutate(
    var = janitor::make_clean_names(
      short_name,
      replace = c(`-` = ""),
      case = "none"
    ) |>
      tolower()
  ) |>
  tidylog::relocate(var, .after = short_name) |>
  dplyr::group_by(class) |>
  dplyr::arrange(
    short_name,
    .by_group = TRUE
  )
gt::gt(edcs_info,
       groupname_col = "class") |>
  gt::sub_values(
    values = c("NA"),
    replacement = ""
  ) |>
  gt::cols_label(
    full_name = "Compound",
    short_name = "Symbol",
    var = "Variable name",
    pubchem_cid = "PubChem CID",
    parental_compound = "Parental compound"
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  ) |>
  gt::tab_style(
    style = gt::cell_borders(
      weight = gt::px(0)
    ),
    locations = list(
      gt::cells_body(),
      gt::cells_stub(),
      gt::cells_row_groups()
    )
  )
```
**Information about non-persistent {{< acr edcs first_use=true >}}, including the full compound name, the standard symbol, the used variable name, the identifier from PubChem, and the parental compound.**
:::

@@
